Informing policy via dynamic models: Cholera in Haiti

### 2023-01-21 ms.Rnw
prepared documents for submission to Arxiv
Added haitipkg zenodo doi

\begin{abstract}
\begin{center}
Working draft, \today
\end{center}

@@

\begin{supplement}
\stitle{Auxiliary software: \code{haitipkg}}
\sdescription{
The \code{haitipkg} R package is maintained in a GitHub repository, \code{jeswheel/haitipkg}. The submitted version of this package will be archived on Zenodo.
The package contains all of the data and code used to create, fit and explore the models presented in this article.
}
\end{supplement}

>>>>

\begin{abstract}
% \begin{center}
% Working draft, \today
% \end{center}

@@

\begin{supplement}
\stitle{Auxiliary software: \code{haitipkg}}
\sdescription{
The \code{haitipkg} R package is maintained in a GitHub repository, \code{jeswheel/haitipkg}. The submitted version of this package is archived on Zenodo: \code{10.5281/zenodo.7557099}
The package contains all of the data and code used to create, fit and explore the models presented in this article.
}
\end{supplement}
